---
title: "Summary of gaussian process analysis so far"
output:
  slidy_presentation:
    duration: 45
    dev: svg
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(tidyr)
library(dplyr)
source('./r-scripts/mung-data.r')
```

## Process so far

* Take data from Jackson
* Train a Gaussian Process classifier to recognise in the "simulations" when a person was viewing the high or the low frequency
* Use this classifier to produce probabilistic output: how likely is a person to have seen the high or low frequency, given any two frequency amplitudes


## Checking the model predicts the right thing

* Summarise the probabilistic output based on what the person actually saw:
    + predicted probability of seeing `High` when they reported
        - `High`
        - `Mixed`
        - `Low`

## Checking the model predicts the right thing
```{r  fig.width=10, fig.height=7, warning=FALSE, eval=TRUE, message=FALSE, tidy=TRUE, dev='png', echo=FALSE, fig.show='hold', fig.align='center'}
source('./r-scripts/plot-prob-in-percept.r', print.eval = TRUE)
```


## What can this model tell us about the strength of dominance?

* Summarise the classifier output based on when in a percept duration it occurred:
    + predicted probability of seeing `High` binned into 10% bins of percept (so first 10%, second 10%, etc)
    + Do this for dominance periods where they reported `High`, `Mixed`, or `Low`
    + Also do this for `Mixed` periods
        - Split mixed periods into whether they were followed by a dominance period of `High` or `Low`


## Correct prediction of percept falls at the end of dominant periods

```{r  fig.width=10, fig.height=7, warning=FALSE, eval=TRUE, message=FALSE, tidy=TRUE, dev='png', echo=FALSE, fig.show='hold', fig.align='center'}
source('./r-scripts/plot-timecourse.r', print.eval = TRUE)
```

## Can it tell us any more about the mixed period?

* Take the prediction of the current percept when the participant actually reports `Mixed`, but split `Mixed` percepts by whether they are followed by a `High` or a `Low` percept
    + Is the subsequent percept already detectable in the current mixed percept?
    + How early can we tell what the next percept will be?

## Prediction consistent with the *following* percept rises during mixed period

```{r  fig.width=10, fig.height=7, warning=FALSE, eval=TRUE, message=FALSE, tidy=TRUE, dev='png', echo=FALSE, fig.show='hold', fig.align='center'}
source('./r-scripts/plot-mix-bynext.r', print.eval = TRUE)
```

## Can we do the same for dominant periods?
* Take the prediction of the current percept when the participant actually reports `High` or `Low`, but split by whether the _next_ percept will be `Mixed`, or the other dominant
    + Is the subsequent percept already detectable in the current dominant percept?
    + How early can we tell what the next percept will be?


## Can we do the same for dominant periods?
```{r  fig.width=10, fig.height=7, warning=FALSE, eval=TRUE, message=FALSE, tidy=TRUE, dev='png', echo=FALSE, fig.show='hold', fig.align='center'}
source('./r-scripts/plot-next-for-dominance.r', print.eval = TRUE)
```

