---
title: "Summary of gaussian process analysis so far"
output:
  slidy_presentation:
    duration: 45
    dev: svg
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(tidyr)
library(dplyr)
source('./r-scripts/mung-data.r')
```

## Process so far

* Take data from Jackson
* Train a Gaussian Process classifier to recognise in the "simulations" when a person was viewing the high or the low frequency
* Use this classifier to produce probabilistic output: how likely is a person to have seen the high or low frequency, given any two estimates of frequency
* Then summarise this probabilistic output based on what the person actually saw:
  + predicted probability of seeing `High` when they reported `High` / `Mixed` / `Low`
* Then summarise the classifier output based on when in a percept duration it occurred:
  + predicted probability of seeing `High` during the first or last 10% of them reporting `High` or `Low`


## Prediction of percept falls during rivalry period

```{r  fig.width=10, fig.height=7, warning=FALSE, eval=TRUE, message=FALSE, tidy=TRUE, dev='png', echo=FALSE, fig.show='hold', fig.align='center'}
source('./r-scripts/plot-timecourse.r', print.eval = TRUE)
```

## Prediction of the *following* percept rises during mixed period

```{r  fig.width=10, fig.height=7, warning=FALSE, eval=TRUE, message=FALSE, tidy=TRUE, dev='png', echo=FALSE, fig.show='hold', fig.align='center'}
source('./r-scripts/plot-nextcourse.r', print.eval = TRUE)
```

